Lifting CDCL to Relational Domains

### 2016-10-13 paper.tex
domain text
domain text updated
CDCL
octagon figure
definitions added
definition of deduction transformer
clauses and literals
decision
decision text
static analysis equation
experiment
abstract

\usepackage{import}
\usepackage{times}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{mathptm}
\usepackage{color}
\usepackage{listings}
\usepackage{verbatim}
\usepackage{comment}
\usepackage{alltt}
\usepackage{psfrag}
\usepackage{epsfig}
\usepackage{wasysym} 
\usepackage{subfigure}
\usepackage{paralist}
\usepackage{dingbat}
\usepackage[algo2e,linesnumbered,ruled,lined]{algorithm2e}
\usepackage{hyperref}
\makeatother

\newcommand{\tool}[1]{\textsc{#1}\xspace}
\newcommand{\cbmcv}{\tool{cbmc 5.0}}
\newcommand{\Omit}[1]{}

@@

\title{Lifting CDCL to Numerical Domains}

\author{Rajdeep Mukherjee\inst{1} Peter Schrammel   Daniel Kroening}

\institute{University of Oxford, UK \and University of Sussex, UK \\
\email{\{rajdeep.mukherjee,kroening\}@cs.ox.ac.uk},
\email{p.schrammel@sussex.ac.uk}}
\Omit {
\author{Rajdeep Mukherjee\inst{1} \and
Peter Schrammel\inst{2} \and
Daniel Kroening\inst{1}}

\institute{University of Oxford, UK \and University of Sussex, UK \\
\email{\{rajdeep.mukherjee,kroening\}@cs.ox.ac.uk},
\email{p.schrammel@sussex.ac.uk}}
}

@@

%===============================================================================
\begin{abstract}
%===============================================================================
%
The Conflict Driven Clause Learning (CDCL) algorithm can be seen as an 
alternation between over-approximate deduction with boolean 
constraint propagation, and under-approximate abduction, with 
conflict analysis.  {\em Abstract Conflict Driven Clause Learning} 
(ACDCL) is a novel program analysis that embeds an abstract domain 
inside the CDCL algorithm. From decision procedure perspective, 
ACDCL is a SAT solver for program analysis constraints and is a 
strict generalisation of propositional CDCL solvers. From Abstract 
Interpretation point of view, ACDCL can be viewed as an abstract 
interpreter that uses decision and learning to increase the precision 
of abstract transformers.  In this paper, we instantiate ACDCL with 
a relational and a non-relational numerical abstract domain and 
evaluate the performance of our analyzer with program verifiers that 
uses propositional-level solvers.  Experimental evidence on a set of 
\rmcmt{N} benchmarks \rmcmt{drawn from X} shows significant reduction 
in the number of decisions and backjumping iterations along with stronger 
deductions and learned clause aided by the richer abstract domains.
%
\end{abstract}
%===============================================================================
\input{introduction}
%===============================================================================

%===============================================================================
\input{background}
%===============================================================================

@@

%===============================================================================
\input{definition}
%===============================================================================

@@

@@

>>>>

\usepackage{import}
\usepackage{times}
\usepackage{array}
\usepackage{graphicx,wrapfig}
\usepackage{cite}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{mathptm}
\usepackage{color}
\usepackage{listings}
\usepackage{verbatim}
\usepackage{comment}
\usepackage{alltt}
\usepackage{psfrag}
\usepackage{epsfig}
\usepackage{wasysym} 
%\usepackage{subfigure}
\usepackage{paralist}
\usepackage{dingbat}
\usepackage[algo2e,linesnumbered,ruled,lined]{algorithm2e}
\usepackage{hyperref}
\makeatother

\newcommand{\tool}[1]{\textsc{#1}\xspace}
\newcommand{\cbmcv}{\tool{cbmc 5.0}}
\newcommand{\Omit}[1]{}
\newcommand{\mydef}[1]{\begin{definition}#1\end{definition}}
\newcommand{\rmcmt}[1]{{\color{magenta}{#1}}}
\newcommand{\pscmt}[1]{{\color{blue}{#1}}}

@@

\title{Lifting CDCL to Relational Domains}

\author{Rajdeep Mukherjee\inst{1}\hskip 1em  Peter Schrammel\inst{2}\hskip 1em  Daniel Kroening\inst{1}}

\institute{University of Oxford, UK \and University of Sussex, UK \\
\email{\{rajdeep.mukherjee,kroening\}@cs.ox.ac.uk},
\email{p.schrammel@sussex.ac.uk}}

@@

%===============================================================================
\begin{abstract}
%===============================================================================
%
  \emph{Abstract Conflict-Driven Learning} (ACDL) is a combination of
  abstract interpretation and the well-known Conflict-Driven Clause
  Learning (CDCL) algorithm that is used in SAT solvers. ACDL has been
  successfully used with non-relational abstract domains such as
  intervals to improve the performance of a solver for floating point
  arithmetic, for instance. 
%
Whereas the
algorithms typically used in SAT solvers can be rather easily
lifted from the Boolean lattice to other non-relational domains,
lifting them to relational domains is challenging.
%because of inter-"literal" dependencies
%because of the weaker properties of "literals"
%
In this paper we present the adaptations of algorithms and heuristics
for propagation, decision making and conflict learning necessary in
order to enable the use with relational domains.
%
We have implemented these algorithms inside the 2LS verification tool
for the example of the template polyhedra domain.
%
We evaluate the performance of our analyzer in comparison with program verifiers that 
uses propositional-level solvers.  Experimental evidence on a set of 
\rmcmt{N} benchmarks \rmcmt{drawn from X} shows significant reduction 
in the number of decisions and backjumping iterations along with stronger 
deductions and learned clause aided by the richer abstract domains.
%
\end{abstract}
%===============================================================================
\input{introduction}
%===============================================================================

%===============================================================================
%\input{background}
%===============================================================================

@@

@@

%===============================================================================
%\input{cdcl}
%===============================================================================

@@

%===============================================================================
%\input{definition}
%===============================================================================
